Bare minimum: set theory

### 2025-09-22 BareMinima/OrderTheory/BareMinimumOrderTheory.tex
Reviewed abstract for bare mininum

\begin{abstract}
A summary overview of order theory, which can be used as a reference, refresher or to be aware of what one does not know.
\end{abstract}

>>>>

\begin{abstract}
	A condensed overview of order theory. Bare minima are meant to give a rough overview, by no means complete, of the subject so that one at least knows what there is to know. It is mainly intended as background for those interested in participating in the Assumptions of Physics (\url{https://assumptionsofphysics.org}) project.
\end{abstract}

### 2025-09-22 BareMinima/SetTheory/BareMinimumSetTheory.tex
SetTheory: moving families at the end of the first section
Reviewed abstract for bare mininum

\begin{abstract}
This note presents a condensed summary of set theory which can function as a crash course, refresher and/or reference. Bare minima are meant to give a rough overview, by no means complete, of the subject to the intellectually curious, particularly in the context of foundational questions in physics. This work is part of Assumptions of Physics (\url{https://assumptionsofphysics.org}), a project that aims to identify a handful of physical principles from which the basic laws can be rigorously derived.
\end{abstract}

>>>>

\begin{abstract}
A condensed overview of set theory. Bare minima are meant to give a rough overview, by no means complete, of the subject so that one at least knows what there is to know. It is mainly intended as background for those interested in participating in the Assumptions of Physics (\url{https://assumptionsofphysics.org}) project.
\end{abstract}
